\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-22 Report/notes.tex
put some order in the report folder
new plot

	\begin{figure}
		\centering
		\includegraphics[width=12cm]{faq-erlang.jpg}
		\caption{The effect of $k$, the number of time points within the sequence of exponential transitions, on the shape of the resulting phase-type distribution. Increasing $k$ makes the phase-type distribution more deterministic. This picture was taken from the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{sspqueue.png}
		\caption{The blue line is the result without phase type fitting.}
		\label{fig:res1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{time.png}
		\caption{Computation time for different values of $k$. The growing lines represent computations of models with phase-type distributions. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{size.png}
		\caption{Size of model for different values of $k$.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_hybrid_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_001}
	\end{figure}

>>>>

	\begin{figure}
		\centering
		\includegraphics[width=12cm]{picture/faq-erlang.jpg}
		\caption{The effect of $k$, the number of time points within the sequence of exponential transitions, on the shape of the resulting phase-type distribution. Increasing $k$ makes the phase-type distribution more deterministic. This picture was taken from the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/sspqueue.png}
		\caption{The blue line is the result without phase type fitting.}
		\label{fig:res1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/time.png}
		\caption{Computation time for different values of $k$. The growing lines represent computations of models with phase-type distributions. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/size.png}
		\caption{Size of model for different values of $k$.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using hybrid engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_hybrid_01}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/diff_explicit_01.png}
		\caption{Distance of result of the SSP computation between the event model and the PTF model using explicit engine,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:diff_explicit_001}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/dist02_explicit_01.png}
		\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using explicit engine versus the PTF parameter k,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:dist02_explicit_001}
	\end{figure}
